Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-05-03 paper.tex
Added info about TP,TN,FP,FN, sensitivity and specificity

\section{Results}

>>>>

\section{Results}
TP: The number of cases correctly predicted as occurance of difference \\
FP: The number of cases incorrectly predicted as occurance of difference \\
TN: The number of cases correctly predicted as no occurance of difference \\ 
FN: The number of cases incorrectly predicted as no occurance of difference \\
\[
	    Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
\]
Sensitivity: The ability to predict the differences cases correctly. The bellow formula can be used to calculate sensitivity of a test.
\[
            Sensitivity = \frac{TP}{TP+FN}
\]
Specificity: The ability to predict the non differences cases correctly. The following formula can be used to calculate specificity of a test. 
\[
            Specificity = \frac{TN}{TN+FP}
\]
